An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-03-24 EconGrowthSeminar.Rnw
Now including graphs of CI size vs. parameter value for all of the fits I had been considering.

\begin{frame}{CI and $\gamma$ in Cobb-Douglas} %----------------------------
  Graph here of CI vs. $\gamma$ where each country abbreviation is plotted.
\end{frame}

@@

    \pause
    \item{Direct energy input to economy ($q$)is unimportant as a Cobb-Douglas predictor of economic output ($y$)}
  \end{itemize}
\end{frame}

@@

\begin{frame}{$CI_{\delta}$ and $\delta$ in CES} %----------------------------
  \begin{center}
    \cdeEqn\\
    \includegraphics<1>[height=2.5in]{figure_other/CI-delta-1.pdf}
    \includegraphics<2>[height=2.5in]{figure_other/CI-delta-2.pdf}
    \includegraphics<3>[height=2.5in]{figure_other/CI-delta-3.pdf}
    \includegraphics<4>[height=2.5in]{figure_other/CI-delta-4.pdf}
  \end{center}
\end{frame}

\begin{frame}{$CI_{\delta}$ and $\delta$ in CES} %----------------------------
  Graph here of $CI_{\delta}$ vs. $\delta$ where each country abbreviation is plotted.
\end{frame}

\begin{frame}{$CI_{\sigma}$ and $\sigma$ in CES} %----------------------------
  \begin{center}
    \cdeEqn\\
    \includegraphics<1>[height=2.5in]{figure_other/CI-sigma-1.pdf}
    \includegraphics<2>[height=2.5in]{figure_other/CI-sigma-2.pdf}
    \includegraphics<3>[height=2.5in]{figure_other/CI-sigma-3.pdf}
    \includegraphics<4>[height=2.5in]{figure_other/CI-sigma-4.pdf}
  \end{center}
\end{frame}

\begin{frame}{$CI_{\sigma}$ and $\sigma$ in CES} %----------------------------
  Graph here of $CI_{\sigma}$ vs. $\sigma$ where each country abbreviation is plotted.
\end{frame}

\begin{frame}{Implications from CES} %----------------------------
  \begin{center}\cesEqn\end{center}
  \vspace{\baselineskip}

  \begin{itemize}
    \item{kl and e are complements, sigma small where it is distinguishable.}
    \item{Direct energy input to economy ($q$)is unimportant as a CES predictor of economic output ($y$), because delta is close to 1.0}
  \end{itemize}
\end{frame}

>>>>

\begin{frame}{CI and $\gamma$ in Cobb-Douglas} %----------------------------
<<CI_gamma_vs_gamma_Graph, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
CIvsParamPlot(model="CDe", param="gamma", energyType="Q")
@
\end{frame}

@@

    \pause
    \item{Direct energy input to economy ($q$) is unimportant as a Cobb-Douglas predictor of economic output ($y$)}
  \end{itemize}
\end{frame}

@@

\begin{frame}{$CI_{\delta}$ and $\delta$ in CES} %----------------------------
  \begin{center}
    \small\cesEqn\normalsize\\
    \includegraphics<1>[height=2.5in]{figure_other/CI-delta-1.pdf}
    \includegraphics<2>[height=2.5in]{figure_other/CI-delta-2.pdf}
    \includegraphics<3>[height=2.5in]{figure_other/CI-delta-3.pdf}
    \includegraphics<4>[height=2.5in]{figure_other/CI-delta-4.pdf}
  \end{center}
\end{frame}

\begin{frame}{$CI_{\delta}$ and $\delta$ in CES} %----------------------------
<<CI_delta_vs_delta_Graph, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
CIvsParamPlot(model="CES", param="delta", energyType="Q")
@
\end{frame}

\begin{frame}{$CI_{\sigma}$ and $\sigma$ in CES} %----------------------------
  \begin{center}
    \small\cesEqn\normalsize\\
    \includegraphics<1>[height=2.5in]{figure_other/CI-sigma-1.pdf}
    \includegraphics<2>[height=2.5in]{figure_other/CI-sigma-2.pdf}
    \includegraphics<3>[height=2.5in]{figure_other/CI-sigma-3.pdf}
    \includegraphics<4>[height=2.5in]{figure_other/CI-sigma-4.pdf}
  \end{center}
\end{frame}

\begin{frame}{$CI_{\sigma}$ and $\sigma$ in CES} %----------------------------
<<CI_sigma_vs_sigma_Graph, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
CIvsParamPlot(model="CES", param="sigma", energyType="Q")
@
\end{frame}

\begin{frame}{Implications from CES} %----------------------------
  \begin{center}\small\cesEqn\normalsize\end{center}
  \vspace{\baselineskip}

  \begin{itemize}
    \item{kl and e are complements, sigma small where it is distinguishable.}
    \item{Direct energy input to economy ($q$) is unimportant as a CES predictor of economic output ($y$), because delta is close to 1.0}
  \end{itemize}
\end{frame}
